### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels. 
\begin{adjustbox}{angle=90}

\begin{table*}
%\centering
\caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
\label{table:related_work}
\resizebox{2\columnwidth}{!}{%

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
\end{table*}
\end{adjustbox}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

>>>>

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels.

\begin{sidewaystable}

%\begin{table*}
%\centering
\caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
\label{table:related_work}
\resizebox{1\columnwidth}{!}{%

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
%\end{table*}
\end{sidewaystable}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
